Human Factors Influencing Visual Statistical Inference

### 2015-08-28 sociology_paper.Rnw
map

\begin{figure}[htbp] 
   \centering
%   \includegraphics[width=6.5in]{learning_trend.pdf} 
    \includegraphics[width=3.2in]{practical_impact_graduate.pdf} 
    \includegraphics[width=3.2in]{practical_impact_degree.pdf} 
   \caption{Proportion of correct responses of an 18-25 year old female in the United States with a graduate degree compared to a high school degree. Even though having a graduate degree leads to  statistically significant increase, the effect size in the dependent variable is  0.045 which is  negligible from a practical point of view. The difference diminishes as we move away one or two standard deviations ($\sigma_{\ell} =2.293$) 
   of lineup variability.}
   \label{fig:practical_impact_graduate}
\end{figure}

>>>>

\begin{figure}[htbp] 
   \centering
%   \includegraphics[width=6.5in]{learning_trend.pdf} 
    \includegraphics[width=3.2in]{practical_impact_graduate.pdf} 
    \includegraphics[width=3.2in]{practical_impact_degree.pdf} 
   \caption{Proportion of estimated data identifications by an 18-25 year old female in the United States with a graduate degree compared to a high school degree. Even though having a graduate degree leads to  statistically significant increase, the effect size in the dependent variable is  0.045 which is  negligible from a practical point of view. The difference diminishes as we move away one or two standard deviations ($\sigma_{\ell} =2.293$) 
   of lineup variability.}
   \label{fig:practical_impact_graduate}
\end{figure}
